Title
========================================================

Always use the RMD file to load the data and take all your notes.

```{r}
facebook <- read.delim('pseudo_facebook.tsv')
```

Playing around with facebook's birthday
```{r}
library(ggplot2)
qplot(x= dob_day, data = facebook, bandwidth = 40)+
  scale_x_discrete(breaks=1:31)+
  facet_wrap(~dob_month, ncol = 3)
  facet_grid(~horizontal)
```
***Facet_wrap(formula), it actually takes formula inside its parenthesis. Don't forget the tilde in facet**
Remember how we used to use the facet using open refine. Its the same thing here in R programming as well.

documentation is here <http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/>
default setting in facebook is January 1st

```{r}
library(ggplot2)  
qplot(x= friend_count, data = facebook, xlim = c(0, 1000))
```
the xlim makes sure that i am only seeing the values in x axis from 0- 1000

```{r}
library(ggplot2)
ggplot(aes(x = friend_count), data = facebook, xlim = c(1, 1000)) +
    geom_histogram()
```


this histogram is telling us friend distribution about men and female
```{r}
qplot(x= friend_count, data = facebook, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))+
  facet_wrap(~gender, ncol = 2)
```

Missing values are presented by NA in R.

```{r}
qplot(x= friend_count, data = subset(facebook, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))+
  facet_wrap(~gender, ncol = 2)
```

Creating subsets are extremely important. If you need to filter your data as much as possible.

```{r}
#table(facebook$gender)
by(facebook$friend_count, facebook$gender, summary)
```
table command gives you the total number of males and females we have in the dataset
The result of this ----> by(facebook$friend_count, facebook$gender, summary)
facebook$gender: female
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0      37      96     242     244    4923 
------------------------------------------------------------------------------------ 
facebook$gender: male
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0      27      74     165     182    4917 

median is always a best statistics because it is a more robust way to analyze data. Esp if the data is long tailed.

```{r}
  ggplot(aes(x = tenure), data = facebook) +
  geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```
The parameter color determines the color outline of objects in a plot.
The parameter fill determines the color of the area inside objects in a plot.

```{r}
qplot(x =  tenure, data = facebook, color = I('black'), fill = I('#099DD9'))
```
so the color black determines the outline whereas the parameter fill determines the color of the area inside

```{r}
qplot(x =  tenure/365, data = facebook, binwidth = 2.5, color = I('black'), fill = I('#099DD9'))
```

```{r}
ggplot(aes(x = tenure / 365), data = pf) +
  geom_histogram(color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Number of years using Facebook') +
  ylab('Number of users in sample')
```
generating the lables are extremely important.

```{r}
qplot(x =  age, data = facebook, binwidth = 1, color = I('black'), fill = I('#099DD9'))
```

if you want to know the summary of any particular element then you need to use this. It will give you 
median, max, min, mean and other details.
```{r}
summary(facebook$age)
```
Everytime you see the data is not properly distributed then you can use the log of the variable to see the summary 

```{r}
#summary(log10(facebook$age))
summary(sqrt(facebook$friend_count))
```





















































      









