---
title: "decptive_correlation/discrete dividing"
author: "Rakesh"
date: "August 7, 2015"
output: html_document
---

```{r}
ggplot(aes(y= Mitchell$Temp, x=Mitchell$Month), data = Mitchell) + 
  geom_point() + 
  scale_x_discrete(breaks = seq(0, 203, 12))
#if you want to divide your scatter plot into multiple steps then you could do that
```

```{r}
#q plot is superintelligent when it comes to scatter plot
#if you want to know the range of the limits then you can do 
#range(Mitchell$month )
cor.test(Mitchell$Temp, Mitchell$Month)
```


/*
ou could also get perspective on this data by overlaying each year's data on top of each other, giving a clear, generally sinusoidal graph. You can do this by using the R's modulus operator %% in your code. Try running the code below!

ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+
  geom_point()

Data Visualization Pioneers
John Tukey
William Playfair
William Playfair and the Psychology of Graphs

There are other measures of associations that can detect this. The dcor.ttest() function in the energy package implements a non-parametric test of the independence of two variables. The test correctly rejects the independence.*/

