Lesson 4
========================================================
***
### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

When there are two variable in action then you need to visualize using scatter plot

```{r Scatterplots}
qplot(x=age, y=friend_count, data=facebook)
```
#this is the tutorial http://www.ceb-institute.org/bbs/wp-content/uploads/2011/09/handout_ggplot2.pdf
***
If you want to draw the same thing in ggplot then you need to explicitly specify what type of graph are you lookig for. In ggplot we have to use the AES wrapper of X and Y variables as it is shown below. 

```{r}
ggplot(aes(x=age, y=friend_count), data = facebook) + geom_jitter(alpha = 1/20) +
  xlim(13, 90)
summary(facebook$age)
```

if you really want it to look more clear then you can use coord_trans layer. The below code is more easy to read.

```{r}
ggplot(aes(x=age, y=friend_count), data = facebook) + geom_point() +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')
```

# Examine the relationship between
# friendships_initiated (y) and age (x)
# using the ggplot syntax.

# We recommend creating a basic scatter
# plot first to see what the distribution looks like.
# and then adjusting it by adding one layer at a time.

```{r}
ggplot(aes(x=age, y=friendships_initiated), data = facebook) + geom_point()
summary(facebook$friendships_initiated)
```
young people send more friend request then old people as you can see in the data.

DPLYR Package introduction and how it can be used.
http://www.r-bloggers.com/hadley-wickham-presents-dplyr-at-user-2014/

Some of the interesting function that we can look for is fitler(), group_by(), mutate(), arrange()
```{r}
library(dplyr)
age_groups <- group_by(facebook, age) #group my facebook data by age
result <- summarise(age_groups,
                    friend_count_mean = mean(friend_count),
                    friend_count_median = median(friend_count),
                    n = n())

arrange_result <-  arrange(result, age)
head(arrange_result)
```
t are some things that you notice right away?
Response: You could see the number of friends peaked from age 14-15 because we have the mean friend count.
That's the power of this package dplyr
***


# Plot mean friend count vs. age using a line graph.
# Be sure you use the correct variable names
# and the correct data frame. You should be working
# with the new data frame created from the dplyr
# functions. The data frame is called 'pf.fc_by_age'.

don't forget the dataframe which you are using here. intially we are playing aroung with facebook data but now we are using the arrange_result so you need to change that too.

```{r ggplot Syntax}
p <-ggplot(aes(x=arrange_result$age, y=arrange_result$friend_count_mean), data = arrange_result)
p + geom_line()
```
#geom_line is a better figure that geom_point 
***

### Overplotting
Notes:

```{r Overplotting}

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

